\chapter{Goals}
\label{cap:goals}

% • Focus on value 
% • Start where you are 
% • Progress iteratively with feedback 
% • Collaborate and promote visibility  
% • Think and work holistically
% • Keep it simple and practical 
% • Optimize and automate 


The acquisitions of foreign banks represnet new opportunities for the company for expands and improve their services, and sideway to create a better working internal structure. (focus on value)
The IT department plays a strategic role, in ensuring that business services remain reliable, secure and efficient during the transformation and retrieving information about the current state of art (start where you are).
In order to reach the business objective and concretize the bank's vision, the IT department has adopted a structure (stat where you are) as `Shared Service Center'. This means that IT is no longer considered only a technical support function, but cover a proactive service, providing standardized services and ensuring the hight-quality, cost effective of them, across all business division.


The main goal of IT is to implement a `Performance-Based Management' approach. With this model organizational performance is continuously monitored through measurable KPIs, which serve as pillar to base decision.  (progress iteratively with feedback)
Decisions based on objective data retrieved, rather than subjective evaluations, allows management to identify weakness, measure progress and compare it to the strategic objective and continuously improve service quality.



In order to achieve the goals defined, the bank has identified three Critical Success Factors (CSFs) that represent key areas required to success and to put attention and to enforce.

- the first CSF is the `Customer Partnership', since the banks wants to achieve insert goal and cooperate with independent fiancial advisor for example. (collaborate and promote visibility)
In order to create a customer partnership, IT Department aims to collaborate with respective business units (like relationship managament) thus to involve customers closely to into the services provided by the bank it self, thus to individuate through feedback and surveys the customer needs.

- second CSF is `Process Factory', since the bank intends to standardize IT processes, technologies and operational procedures across all the acquired organizations and various departments. 
Standardization reduces complexity, minimize operational waste, simplifies maintenance actiities and improves service consistency. Overall reprensent a value to the bank giving it a clear workflow of the processes. (keep it simple and practical)
This objective is fundamental for the company since the bank operates across multiple countries and must integrate different it environments while maintaining regulatory compliance and service quality

- third CSF is `continuous improvement', the bank reognizes that high-quality services require continuous measurements and optimization. 
Analyzing the data collected (link before) continuous service improvement, one of the core principles of ITIL, enables the organization to reduce operational costs, improve customer satisfaction, optimize resource utilization and support startegic decision-making based on reliable data. 
And allows through small steps to proceed and increase the values of the companies, by proceeding with feedback thus to optimize services and resources providede to the customers. --> Think and work holistically



To evaluate whether these Critical Success Factores are being achieved, the bank has defined a KPI tree composed of six KPI:

Together, these KPIs provide a balanced view of service quality, operational efficency, customer satisfiaction and financial performance.
By monitoring (optimize and auotmate) these indicators on a regular baisis, the IT department can verify that its activities remain aligned with the overral business stretegy and can identify areasw where corrective actions or improvement initiatives are required ---> keep momentum gount and service level management








Basically consent to answer to the questions `Where we are?' and `Did we get there?' of the SVS principles.
In fact these principles should serve as a framework to identify the goals and strategic plan

- whats the vision? answered before
- where do we want to be::: make the list
- how we get there?
- take actions
- did we get there?
- keep the momentum going --> continuous improvement
