\chapter{Critical Success Factors}
\label{cap:criticalsuccessfactors}

Critical Success Factors (CSFs) represent the limited number of areas in which satisfactory performance is essential for an organization to achieve its strategic objectives and business goals. Within the context of IT Service Management (ITSM) and Performance-Based Management, CSFs provide a structured mechanism for translating the organization's strategic vision into measurable operational outcomes. They identify the key domains that require continuous attention, monitoring, and improvement to ensure that the organization's mission and strategic objectives are successfully achieved.

For the bank's IT Department, which aims to operate as a Shared Service Center delivering high-quality and cost-effective IT services, Critical Success Factors serve as the foundation for defining performance expectations and establishing appropriate Key Performance Indicators (KPIs). By aligning operational activities, ITSM processes, and performance measurements with these critical areas, the organization can effectively monitor progress, support decision-making, and drive continual service improvement. The following sections analyze each Critical Success Factor individually, identifying the associated KPIs, suitable metrics, and the ITSM processes that influence their performance.
% SAVAS FIX


\section{Customer Partnership}

Customer Partnership represents an important and strategic pillar to accomplish the Bank's goals. The IT Department must establish measurable relationships between external customers and other stakeholders, assuming a role that actively contributes to the improvement of the services provided and, in specific, monitors through KPIs the value perceived by customers.
The IT has to collaborate also internally within the organization in order to engage the appropriate department whenever it is needed.



This topic is fundamental for the success of the Bank's vision, because the international expansion through acquisitions and other partnerships introduces new business requirements due to different customer expectations, cultural diversity, and increased service complexity.
These challenges must be supported in a proactive way, by ensuring that IT services remain aligned with business objectives, deliver consistent value across different countries, and contribute to the Bank's growth, while complying with agreed Service Level Agreements between customers, stakeholders and user expectations.




These requisites, makes performance measurement crucial. By continuously monitoring and collecting customer-oriented metrics and analyzing services scores, IT Department is able to implement a continual service improvements that can strengthen customer trust and enrich the service quality. Gaining long-term partneship.
This customer-centric approach supports organization's objectives of delivering high-performance, high-quality and cost-effective IT services. Aimed toward to accomplish the predefined goals \ref{cap:goals}



\subsection{Time To Market}
\label{subs:timetomarket}
%   Savas

Time to market, also known as Speed to Market is made operational through \textbf{Average Lead Time for Change to Production} KPI metric, defines as the elapsed time between formal approval of a business requirement and its deployment into the production environment. This metric is selected because it directly reflects the organization’s ability to translate customer and business demands into operational banking capabilities which is essential for achieving the stated rapid digital service evolution and revenue growth objectives of the organisation. In the context of the strategic goal of the organisation is to increase the income from internet banking, reduced Time to Market provides higher organizational agility and faster delivery of customer targeting features, thus improving market responsiveness and competitive positioning.

There are several ITIL aligned ITSM processes that primarily effects Time to Market:

\begin{itemize}
    \item \textbf{Change enablement} has a direct effect through approval workflows and Risk Management procedures, were excessive governance overhead can result in significant delays.
    \item \textbf{Release and Deployment Management} also effects the indicator  as deployment scheduling , release batching and automation maturity determine how quickly the validated changes end up deployed in the production.
    \item \textbf{Service Validation and Testing} influences Lead Time through test cycle duration and error handling loops, which can create bottlenecks if automation coverage is insufficient.
    \item \textbf{Service Design and Transition} activities also effect indirectly throught the time required for requirement analysis, architectural validation, and coordination of technical dependencies.
\end{itemize}

Overall, inefficiencies or lack of cooperation across these processes will result in the increase of Lead Time, where higher process integration, standardization and automation would reduce it, resulting with the improvement of Time To Market KPI.

%   DONE but check

\subsection{Performance To Contract}
\label{subs:performancetocontract}
% PerformanceToContract --> Alberto

Performance to Contract focuses on the IT Department`s ability to respect contractual obligations and consistently deliver services according to the agreements made with customers and explained in natural language in the SLAs. \\

This subject requires IT services to meet the agreed levels of different measurable values, such as availability, reliability, responsiveness, and quality, while ensuring and supporting the Bank's operational and predefined business objectives.


% TODO - make a list of definitions, to take more space?? 
% \begin{itemize}
%     \item \textbf{availability}: 
%     \item \textbf{reliability}:
%     \item \textbf{responsiveness}:
%     \item \textbf{quality}: 
    
% \end{itemize}

Well-defined Key Performance Indicators ensure evidence of whether service targets are being achieved and enable the IT department to identify eventual deviations or deficiencies. This gives a clear input to potential corrective actions or improvements to service performance over time. Moreover, the monitoring of performance against contractual commitments also increases transparency and accountability between IT and different business units or external third-party service providers.


This process is fundamental and very important for the Bank, because many banking services, such as Online Banking, ATMs, global payments, or other third-party services, depend strictly on service levels and regulatory compliance. Also, through a cybersecurity point of view, the respect of performance is fundamental to prevent various cyber-attacks and potential disservices.\\
In addition, being a global Bank, the services must be ensured not only during the local time of the main Headquarters, but the support must be available respecting different cultural scenarios, thus supporting suppliers or international partners.


As a result of continuously measuring contractual performance and acting on the collected data, IT Department can improve service reliability, reduce the risk of SLA breaches and improve the overall customer relationships and partnerships with various stakeholders.


\section{Process Factory}
%   Savas

The Process Factory CSF approach is required in order to transform the IT department into a Shared Service Center, where IT Services are delivered through standardized, repeatable, and performance-oriented processes. This CSF is important considering the bank's international expansion strategy, the integration of acquired oversees banks and the consolidation of support functions within the Shared Services  Division.

%   Still WIP


% Savas 

% From Alberto:
The Process Factory approach aims to standardize IT Service Management (ITSM) processes in order to deliver services with greater efficiency, higher quality, and lower operational costs. Within this approach, one of the primary objectives is the systematic identification and elimination of waste, defined as any activity that consumes resources without creating value for customers or supporting business objectives. Moreover the standardization of process helps the creation of waste and redundant steps or activities....to be continued/reviewed


\subsection{Standardization}
\label{subs:standardization}
%   Savas


\begin{itemize}
    \item 
\end{itemize}

%   Still WIP

\subsection{Waste}
\label{subs:waste}

With the term \textbf{waste} IT Service Management intend every activioty that consumes time, effort or financial resources without increasing the value delivered to the customer. From Lean methodology and ITIL perspective, customers only perceive value when an IT service is available, reliable, secure and supports the desired utility functions. 
Any process that do not contribute to outcomes is considered waste and should be minimized or eliminated (\textit{as the guiding principles suggests: ``Keep it simple and practical''}).

Waste includes more than obvious failures, such as services outages but also hidden inefficiencies embedded in recurrent operations. These may include redudant processes steps, unnecessary approvals, excessive manual work, repeated incident resolution, but even the collections of data taht is never used to improve services.\\
Such activities increase opreational costs, reducing productivity and delaying service delivery, impact negatively ithe customer satisfaction.

Lean thinking identifies different categories of waste that can be directly applied to IT Service Management, such as:
\begin{itemize}
    \item \textbf{Waiting}: delays caused by approvals, unavailable personnel or dependencies between teams. \textit{Waiting increases lead time without adding value.}
    \item \textbf{Defects}: errors that require correction, like failed software releases, configuration mistakes, security vulnerabilities, or inaccurate service records.
    \item \textbf{Overprocessing}: performing more work than necessary, including excessive documentation not required or needed by stakeholders. Even unnecessary or redundant approvals, or too many resources allocated to simple activities (often wrongly added near to a delivery deadline).
    \item \textbf{Unused talents}: failing to involve employees with valuable expertise in process improvement, service design or decision-making. \textit{Opposing the ``Collaborate and promote visibility'' guiding principle.}
    \item \textbf{Inventory}: backlogs of unresolved incidents, accumulated change requests, unused hardware, and outdated or unused retreived information.
\end{itemize}

These concepts can be applied through concrete examples to the Bank's use case scenario. For instance, without a structured \textbf{knowledge management} that holds documentation and reusable knowledge, service desk analysts and technical staff repeatedly solve the same problems independently. This duplication of effort represents both overprocessing and inventory waste, increasing incident resolution times and reducing overall efficiency.\\
Another source of waste comes from poor involvement of internal customers during the Service Transition and Service Design, as a result a lot of misunderstandings and usability issues could emerge that converge into rework, additional testing, and corrective changes. This represents both waiting and defects of a service, since problems are identified later in the service lifecycle or already in a production environment

An important aspect that the Bank needs to handle, thus avoiding waste, is due to the expansion into different countries. Social aspects such as language, culture, time zones, and organizational practices could end up creating a bottleneck for the communication system, delaying the throughput of information and slowing incident resolution, change approvals, or decision-making.


Even the differences in operational practices, in the absence of standardized processes \ref{subs:standardization}, could represent a duplication of work and the creation of organizational silos, which can slow down decisions taken toward goal realization, representing the opposite of one of \textit{ITIL core guiding principle ``Think and work holistically''}.
For the Bank, reducing waste is a necessity that allows IT resources to focus on innovation, improvements in service quality and lower operating costs. In order to individuate waste, the organization must ensure standardization of processes, automate repetitive activities, define responsibilities and continuously monitor performance through KPIs (analyzed in the following chapter ??). This transformation of strategy makes the IT department operate as a ``Shared Service Center'' that provides high performance, high quality and cost-effectiveness, aligned with the organization's goals.


\section{Continuous Improvement}
\label{sec:continuousimprovement}



%   Savas

\subsection{Service Costs}
\label{subs:servicecosts}
%   Savas

\subsection{Backlog}
\label{subs:backlog}

%   Alberto

Backlog represnets a structured and prioritized repository of improvements initiatives taken or identified through service performance measurement methods like KPI monitoring, incidents, problem analysis or customer feedback and reviews.
Provide a governance mechanism that enables the organization to systematically collect, evaluate, pripritize and monitor the improvement process and opportunities in a shared system rather than operate as an organizational silos.
In fact, backlog represent a key tool for the transformation of the IT Department into a ``Shared Service Center'', because improvement initiatives are continuously generated from the monitoring of KPI across various processes. The adoption of a welformed backlog gives the IT the possibility to provide and suggest different initiatives thus to ensure the investments of resource and operation that contribute directly to the organization's goals and  support informed decision-making.

Initiatives are prioritized by different factors, such as:
\begin{itemize}
    \item \textbf{Business value} that provide to the customers
    \item \textbf{Strategic alignment} toward organisation's goals
    \item \textbf{Implementation effort}
    \item \textbf{Operational risk}
    \item \textbf{Expected benefits }
    \item \textbf{Resouce ability}
\end{itemize}

The backlog must be continuously reviewed as part of the \textit{Continual Service Improvement} process, allowing new opportunities to be integrated while completed activities can be evaluated against predefined performance indicators.
The outcome of each implemented improvement is measured through opportune KPIs to verify and then support the validation of the achievement of the expected benefits. Moreover, can serve to identify additional optimization and creating a feedback loop that promotes organizational learning and maturity.


Applied to the Bank current ITSM environment, the adoption of an improvement backlog brings several benefits to the services provided, such as:
\begin{itemize}
    \item Enrich and consolidate a Knowledge Management
    \item Increase customer involvement during Service Transition
    \item Introduce formal change evaluation process 
    \item Promote proactive Problem Management
    \item Standardize operational process across international branches and improve collaboration between departments
\end{itemize}

Together, these initiatives contribute the reducing of operational waste while improving service quality, increasing process efficiency and supporting Banks's international growth strategy through a culture of continuous improvement.
