\chapter{Measurement Procedures}
\label{cap:measurementprocedures}


\section{Time to Market}
%   Savas

\subsection{Average Lead Time for Change to Production}

Average Lead Time of Change to Production measures the average amount of time taken for a new or modified IT service, feature, or change to progress from formal approval to successful deployment into the production environment. The metric evaluates the IT department's ability to rapidly deliver business value and respond to customer and market requirements. The reduction in lead time indicates increased organizational agility, improved collaboration between business and IT, and greater effectiveness of the service delivery process. \\

The Average Lead Time of Change to Production was selected because it directly measures the bank's ability to rapidly deliver new and modified digital services to customers. Considering the organization's strategic objectives of international expansion and increasing internet banking revenues, reducing the lead time of service deployment contributes directly to customer satisfaction, competitive advantage, and business agility. This metric is primarily influenced by the Service Design, Change Enablement, Release and Deployment Management, and Service Validation and Testing processes. \\

\begin{table}[h]
    \centering
    \renewcommand{\arraystretch}{1.6}
    \setlength{\arrayrulewidth}{0.6pt}

    \begin{tabularx}{\textwidth}{|X|X|}
    \hline
    \multicolumn{2}{|c|}{\cellcolor{mcblue}\textcolor{white}{\textbf{Average Lead Time for Change to Production}}} \\ \hline

    \rowcolor{mclightgray}
    \textbf{Description} & \textbf{Unit} \\ \hline
    Average time required for a new or modified IT service, feature or change to progress from a formal approval to successful deployment to the production. &
    Days. \\ \hline

    \rowcolor{mclightgray}
    \textbf{Formula} & \textbf{Frequency} \\ \hline
    \[
       \frac{\sum (\text{Deployment Date} - \text{Approval Date})}{\text{\# of Successfully Implemented Changes}}
    \]
     &
    Monthly reporting with quarterly trend analysis. \\ \hline

    \end{tabularx}

    \caption{Measurement - Average Lead Time for Change to Production}
    \label{tab:measurement_AverageLeadTimeforChangetoProduction}
\end{table}

\section{Performance to Contract} 
%   Alberto
Explained in subsection \ref{subs:performancetocontract}.

\subsection{SLA Compliance Rate}
\label{sub:slaComplianceRate}

SLA Compliance Rate can provide a measure whether contractual service levels are respected, thus to accomplish the agreements made with customers or stakeholders and therefore maintaint the quality of the service provided.


For this ~\gls{kpi} the process affected are:
\begin{itemize}
    \item \textbf{Service Level Management}: to ensure an opportune level of service provided that should ensure what agreed in SLA.
    \item \textbf{Incident Management}: to ensure that eventual incident are resolved and the serivce restored to its normal operativity and agreed quality.
    \item \textbf{Request Fulfillment}: to gather and fulfill customer and user requests and making it sure to accomplish them
    \item \textbf{Availabiliy Management}: to ensure the service is available for the user and the downtime dued to incidents or maintenance do not take more than necessary resources (time and costs).\\ 
    The availability of the service can be expressed via the forumla: 
    \[
        \text{Availabiliy} = \frac{\text{AST - downtime}}{AST} \times 100
    \]
    Where ``AST'' indicate the Agreed Service Time, which measure the expectation of the time that service is available; downtime should be included within this value.
    \item \textbf{Capacity Management}: to monitor and ensure that service achieve agreed and exprected performance, satisfying current and future demand in a cost-eﬀective way.
    \item \textbf{Supplier Management}: To ensure that the organization`s suppliers and their performances are managed appropriately to support the seamless provision of quality products and services.
\end{itemize}


\begin{table}[h]
    \centering
    \renewcommand{\arraystretch}{1.6}
    \setlength{\arrayrulewidth}{0.6pt}

    \begin{tabularx}{\textwidth}{|X|X|}
    \hline
    \multicolumn{2}{|c|}{\cellcolor{mcblue}\textcolor{white}{\textbf{SLA Compliance Rate}}} \\ \hline

    \rowcolor{mclightgray}
    \textbf{Description} & \textbf{Unit} \\ \hline
    Percentage of request solved respecting SLAs specification, where is desired a high percentage. &
    Percentage. \\ \hline

    \rowcolor{mclightgray}
    \textbf{Formula} & \textbf{Frequency} \\ \hline
    \[
        \frac{\text{Requests solved within SLA}}{\text{Total requests}} \times 100
    \]
     &
    Monthly. \\ \hline

    \end{tabularx}

    \caption{Measurement - SLA Compliance Rate}
    \label{tab:measurement_SLAComplianceRate}
\end{table}


\subsection{Mean time for restoring service}

Another Key Performance Indicator which can help the IT Department toward the monitor service performance within the expectation of the stakeholders is the measurement of the restoring service time.
This indicator measures how quickly the IT organization restores service after an interruption, closely related to the previous metric~\ref{sub:slaComplianceRate} but can be adopted by IT Department as an input for continuous improvement toward to optimize its response for incidents.

Primarily involves the \textbf{``Incident Management''} process but can be extended to others related process such as:
\begin{itemize}
    \item \textbf{Problem Management} which cover the role to resolve the problems that caused the incident
    \item \textbf{Service Desks} which represent a single point of contact for users and other stakeholders, incident reports should pass by this department, which can be involved within the incident managament and classification then consume time and enter within the metric
\end{itemize}

\begin{table}[H]
    \centering
    \renewcommand{\arraystretch}{1.6}
    \setlength{\arrayrulewidth}{0.6pt}

    \begin{tabularx}{\textwidth}{|X|X|}
    \hline
    \multicolumn{2}{|c|}{\cellcolor{mcblue}\textcolor{white}{\textbf{Mean time for restoring service}}} \\ \hline

    \rowcolor{mclightgray}
    \textbf{Description} & \textbf{Unit} \\ \hline
    Provide the average time required to restore an IT service after an incident has been reported. Lower values indicate better operational perforance and higher compliace with contractual SLAs.
     &
    Minutes. \\ \hline

    \rowcolor{mclightgray}
    \textbf{Formula} & \textbf{Frequency} \\ \hline
    \[
     \frac{\sum{\text{Restoration time}}}{\text{Number of resolved incidents}}
    \]
    
     &
    Weekly (operational team) \& Montly (as management reporting). \\ \hline

    \end{tabularx}

    \caption{Measurement - Backlog Priority Distribution}
    \label{tab:measurement_meanTimeRestoringService}
\end{table}



% ---------------------------------------------------------


\section{Standardization}
%   Savas

\subsection{Standardization Compliance Rate}

Within the context of the bank's transformation toward a shared service center model, standardization of IT services and underlying infrastructure constitutes a fundamental control mechanism for achieving operational efficiency, scalability, and regulatory consistency across geographically distributed units and acquired entities. Given the bank's expansion strategy and the integration challenges arising from heterogeneous legacy systems, variations in service delivery practices, and differing national operating environments, a measurable approach to architectural conformity is required. The selected KPI—percentage of IT services complying with standardized service and enterprise infrastructure architectures—captures the degree to which services adhere to approved reference architectures, standardized deployment models (including the ``virtual first'' principle), and centrally governed configuration baselines. This indicator therefore functions as a proxy for industrialization maturity within the IT organization, directly reflecting the success of the Process Factory pillar in reducing structural variability, improving interoperability, and enabling controlled, repeatable service delivery across all operational domains. \\


\begin{table}[h]
    \centering
    \renewcommand{\arraystretch}{1.6}
    \setlength{\arrayrulewidth}{0.6pt}

    \begin{tabularx}{\textwidth}{|X|X|}
    \hline
    \multicolumn{2}{|c|}{\cellcolor{mcblue}\textcolor{white}{\textbf{Standardization Compliance Rate}}} \\ \hline

    \rowcolor{mclightgray}
    \textbf{Description} & \textbf{Unit} \\ \hline
    Percentage of IT services complying with standardized service and infrastructure architectures. &
    Percentage. \\ \hline

    \rowcolor{mclightgray}
    \textbf{Formula} & \textbf{Frequency} \\ \hline
    \[
        \frac{\text{Compliant IT services}}{\text{Total IT services assessed}} \times 100
    \]
     &
    Quarterly, Monthly, Bianually \\ \hline

    \end{tabularx}

    \caption{Measurement - Standardization Compliance Rate}
    \label{tab:measurement_StandardizationComplianceRate}
\end{table}

Overall, this KPI supports the Process Factory critical success factor by ensuring that IT services are not only delivered efficiently but are also structurally consistent, enabling economies of scale, improved governance, and reduced complexity across the bank`s global IT operations. \\

%   Done but check bc there were some more thing i was CONSIDERING to add.


\section{Waste}
%   Alberto

\subsection{Repeated Incident rate}

    To measure how many incident occur dued to problems that are not already been resolved.\\
    ITSM process involved are:

    \begin{itemize}
        \item \textbf{Incident Management} which is accountable to register the incident and potential workaround used in restoring the service
        \item \textbf{Problem Management} to identify the potential and actual causes of indicents (or known errors) and reduce the probability of the impacts by providing the solutions and workarounds.
        \item \textbf{Knowledge Management} that maintain and improve the eﬀective, efficient, convenient use of information and knowledge across the organization
        \item \textbf{Continual Improvement} in order to increase the value overall the performance and quality of the service
    \end{itemize}

    \begin{table}[h]
        \centering
        \renewcommand{\arraystretch}{1.6}
        \setlength{\arrayrulewidth}{0.6pt}

        \begin{tabularx}{\textwidth}{|X|X|}
        \hline
        \multicolumn{2}{|c|}{\cellcolor{mcblue}\textcolor{white}{\textbf{Repeated Incident Rate}}} \\ \hline

        \rowcolor{mclightgray}
        \textbf{Description} & \textbf{Unit} \\ \hline
        A high value indicate a wasted effort since the cause of the incident has not been eliminated. &
        Percentage. \\ \hline

        \rowcolor{mclightgray}
        \textbf{Formula} & \textbf{Frequency} \\ \hline
        \[
            \frac{\text{Recurring incidents}}{\text{Total incidents}} \times 100
        \]

        &
        Weekly/Monthly. \\ \hline

        \end{tabularx}

        \caption{Waste - Repeated Incident Rate}
        \label{tab:measurement_RepeatedIncident}
    \end{table}


\subsection{Rework rate}

    For instance, since the Bank aims to increase revenue from its Internet Banking services, poor user experience caused by application malfunctions or insufficient service quality may reduce customer engagement. At the same time, these defects can represent significant rework for both external suppliers and the internal design and development teams; increasing costs and delaying service improvements, reducing the overall efficiency of the Service Value Chain (SVC).

    The rate of the rework activities serve a strong KPI for user engagement and involves many process of IT Service Management, main of them are:
    \begin{itemize}
        \item \textbf{Change Enablement}: which have to maximize the number of successful service and product changes by:
        \begin{enumerate}
            \item ensuring that risks have been properly assessed
            \item authorizing changes to proceed
            \item managing the change schedule
        \end{enumerate}
        \item \textbf{Service Validation and Testing}: in order to check that the service meets the desired customer requests.
        \item \textbf{Release Management}: that has the purpose of moving new or changed hardware, software,documentation,processes or any other component to live environments. In this case, needs to apply the reworked services in production.
    \end{itemize}


        \begin{table}[H]
        \centering
        \renewcommand{\arraystretch}{1.6}
        \setlength{\arrayrulewidth}{0.6pt}

        \begin{tabularx}{\textwidth}{|X|X|}
        \hline
        \multicolumn{2}{|c|}{\cellcolor{mcblue}\textcolor{white}{\textbf{Rework Rate}}} \\ \hline

        \rowcolor{mclightgray}
        \textbf{Description} & \textbf{Unit} \\ \hline
        Indicate how many activities and work item needs a rework. Higher value indicated inefficiency and waste. &
        Percentage. \\ \hline

        \rowcolor{mclightgray}
        \textbf{Formula} & \textbf{Frequency} \\ \hline
        \[
            \frac{\text{Work task reopened}}{\text{Total completed work task}} \times 100
        \]

        &
        Montly. \\ \hline

        \end{tabularx}

        \caption{Waste - Rework Rate}
        \label{tab:measurement_NUMofOpenIncident}
        \end{table}


% ---------------------------------------------------------

\section{Service Costs}
%   Savas

\subsection{IT Service costs distribution}

Total IT Service Cost per Service (TISCS) measures the complete financial cost associated with delivering and maintaining a specific IT service over a defined period. This metric provides a service-oriented view of IT expenditure by allocating both direct and indirect costs to individual services within the IT service portfolio. Unlike traditional IT budget measurements, which focus on aggregate spending, TISCS enables management to understand the actual cost of operating each service and to identify opportunities for cost optimization and efficiency improvements.

    \begin{table}[h]
        \centering
        \renewcommand{\arraystretch}{1.6}
        \setlength{\arrayrulewidth}{0.6pt}

        \begin{tabularx}{\textwidth}{|X|X|}
        \hline
        \multicolumn{2}{|c|}{\cellcolor{mcblue}\textcolor{white}{\textbf{Total IT Service Cost per Service}}} \\ \hline

        \rowcolor{mclightgray}
        \textbf{Description} & \textbf{Unit} \\ \hline
        Measures the total cost incurred by the IT organization to deliver, operate, support, and maintain an IT service during a defined reporting period. &
        Currency per service, per reporting period \\ \hline

        \rowcolor{mclightgray}
        \textbf{Formula} & \textbf{Frequency} \\ \hline
        Direct Service Costs + Allocated Indirect Costs &
        Monthly/Quarterly/Annually. \\ \hline

        \end{tabularx}

        \caption{Measurement - Total IT Service Cost per Service}
        \label{tab:measurement_ITcostperservice}
    \end{table}

In the formulation of this KPI metric, Direct Service Costs and Allocated Indirect Cost elements can be listed as following:

\textbf{Direct Service Costs include:}
\begin{itemize}
    \item Infrastructure and hardware costs
    \item Software licensing costs
    \item Application maintenance costs
    \item Personnel and support staff costs
    \item Third-party supplier and outsourcing costs
\end{itemize}

\textbf{Allocated Indirect Costs include:}
\begin{itemize}
    \item Shared infrastructure costs
    \item Service management tooling costs
    \item Facilities and data center costs
    \item Administrative overhead costs
    \item Shared services costs
\end{itemize}


This metric measures the total cost incurred by the IT organization to deliver, operate, support, and maintain a specific IT service during a defined reporting period. The calculation includes all direct costs attributable to the service as well as allocated indirect costs arising from shared resources and support functions.

%   DONE but check again

\section{Backlog}
%   Alberto

% \subsection{Number of open requests}


\subsection{Priority distribution}
\label{sub:prioritydistribution}
Backlog priority distribution measures the compositiion of open tickets, grouping them by their priority. This metric can be applied to different subjects, such as problems or change requests.

With this KPI~\gls{kpi}, the IT can monitor a rank of the amount of task for each division in way to plan and coordinate different resources in order to accomplish first critical tasks and to direct others requests.

It affects several \gls{itsm} process for each division, for instance:

\begin{itemize}
    \item \textbf{Incident Management} for incidents 
    \item \textbf{Problem Management} for problems and known errors
    \item \textbf{Change Enablement} for change requests open or request awaiting to be accomplished
\end{itemize}

\begin{table}[h]
    \centering
    \renewcommand{\arraystretch}{1.6}
    \setlength{\arrayrulewidth}{0.6pt}

    \begin{tabularx}{\textwidth}{|X|X|}
    \hline
    \multicolumn{2}{|c|}{\cellcolor{mcblue}\textcolor{white}{\textbf{Backlog Priority Distribution}}} \\ \hline

    \rowcolor{mclightgray}
    \textbf{Description} & \textbf{Unit} \\ \hline
    Helps determine whether unresolved work is concentrated on high-impact issues and supports prioritization decisions. The organization should aims to lower percentage on the priority level. &
    Percentage. \\ \hline

    \rowcolor{mclightgray}
    \textbf{Formula} & \textbf{Frequency} \\ \hline
    \[
     \frac{\text{Open tickets of priority P}}{Total open tickets} \times 100
    \]
    
    \textit{calculated for each priority level}
    
     &
    Weekly (operational team) \& Montly (as management reporting). \\ \hline

    \end{tabularx}

    \caption{Measurement - Backlog Priority Distribution}
    \label{tab:measurement_backlogPriorityDistribution}
\end{table}



\subsection{Task completed from last report}

Another metric, combined with the before Priority Distribution \ref{sub:prioritydistribution}, provide the work tasks successfully completed during the reporting period. \\
This provide the performance of the various department toward the resolution and accomplishment of the open requests. \\
IT Department should aim to higher percentage expecially related to high priority tasks.

\begin{table}[H]
    \centering
    \renewcommand{\arraystretch}{1.6}
    \setlength{\arrayrulewidth}{0.6pt}

    \begin{tabularx}{\textwidth}{|X|X|}
    \hline
    \multicolumn{2}{|c|}{\cellcolor{mcblue}\textcolor{white}{\textbf{Task Completed Since Last Report}}} \\ \hline

    \rowcolor{mclightgray}
    \textbf{Description} & \textbf{Unit} \\ \hline
    It indicates the team`s throughput and ability to reduce backlog. High percentage means high efficiency of the teams` abilities &
    Percentage. \\ \hline

    \rowcolor{mclightgray}
    \textbf{Formula} & \textbf{Frequency} \\ \hline
    \[
     \frac{\text{Tickets completed during last report}}{Tickets opened during last report} \times 100
    \]
    \textit{divided for each priority level if used as comparison within the previous KPI}
     &
    Montly (within the previous management report). \\ \hline

    \end{tabularx}

    \caption{Measurement - Task Completed Since Last Report}
    \label{tab:TaskCompletedLastReport}
\end{table}